Supplementary Materials

### 2018-12-11 Manuscript/sup_mat/sup_mat.Rmd
changes to sup_mat
Added some more information and sorted plots

# Participants
```{r Participants, echo = FALSE}
# sort out participants 
ls_acc_RT$observer <- as.numeric(as.factor(as.numeric(ls_acc_RT$observer)))

@@

@@

```{r fig1, fig.cap = "\\label{fig1} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt
```

```{r fig2, fig.cap = "\\label{fig2} Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt <- ls_acc_RT %>%
  ggplot(aes(rt)) + 
  geom_histogram() + 
  theme_bw() +  
  facet_wrap(~targSide)
plt$labels$x <- "Response Time (msecs)"
plt2 <- ls_acc_RT %>%
  mutate(log2_RT = log2(rt)) %>%
  ggplot(aes(log2_RT)) + 
  geom_histogram() + 
  theme_bw() +
  facet_wrap(~ targSide)
plt2$labels$x <- "log2 Response Time"

@@

## Split-Half 
`r invalid_kp` trials with invalid key responses were removed. After removing data from the four outlier participants (see above), all remaining incorrect trials `r #find out what this number is meant to be` (n = 2529) were removed, leaving a total of `r nrow(trlDat_unf) - invalid_kp` trials over 60 participants.

>>>>

# Methods 
## Split-Half
In this task, a chin rest with forehead bar was used in order to ensure a viewing distance of 47cm. Participants' fixations were tracked using a deskmounted Eylink 1000 (version 4.594) to record eye position at 1000 Hz. Prior to every block, a 9-point calibration was carried out. This task lasted approximately 30 minutes.

The line segments subtended approximately 1.6&deg; of visual angle.

Any other details needed?

## Adaptive Choice
For this task, participants were sat approximately 47cm from the screen though no chin rest was used to ensure a constant viewing distance. Participants were give 10 practice trials (check this) before starting the actual experiment. (Check how many blocks as well). Participants were told they were to search for a target number (2-5 inclusive). There would be two of these target numbers on every trial; one in a blue square and one in a red square. They were told they only needed to report one of these numbers. The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively). Participants were instructed to be as fast and accuracte as possible. They were also told there would be a tone if they were to report a number that was not present within any of the boxes matching the two target colours.

## Foraging 
Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately. There were (get number of objects on display, I think it was 40?), half of which were the targets for that trial. The squares and circles subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).

Before starting the experiment, participants had 10 (check this number) practice trials to familiarise themeselves with the task. After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition. This took approximately 20 minutes.

# Participants

```{r Participants, echo = FALSE}
# sort out participants 
ls_acc_RT$observer <- as.numeric(as.factor(as.numeric(ls_acc_RT$observer)))

@@

#### get number of incorrect trials ####
incorrect_trials <- ls_acc_RT %>%
  filter(observer != 15,
         observer != 25,
         observer != 47,
         observer != 48,
         responseKey != "Key_x") %>%
  group_by(accuracy) %>%
  summarise(n = n())

@@

```{r acc_plt, fig.cap = "Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt
```

```{r rt_plt, fig.cap = "Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt <- ls_acc_RT %>%
  ggplot(aes(rt)) + 
  geom_histogram() + 
  theme_bw() +  
  facet_wrap(~targSide)
plt$labels$x <- "Response Time (msecs)"
plt2 <- ls_acc_RT %>%
  mutate(log2_RT = log2(rt)) %>%
  ggplot(aes(log2_RT)) + 
  geom_histogram() + 
  theme_bw() +
  facet_wrap(~ targSide)
plt2$labels$x <- "log2 Response Time"

@@

## Split-Half 
`r invalid_kp` trials with invalid key responses were removed. After removing data from the four outlier participants (see above), all remaining incorrect trials (n = `r incorrect_trials$n[incorrect_trials$accuracy == 0]`) were removed, leaving a total of `r incorrect_trials$n[incorrect_trials$accuracy == 1]` trials over 60 participants.
